---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
conditions <- list.files("../to_store/")[1:2]

```


```{r}
lookup_table <- data.frame()
for (my_condition in conditions){
  # split the string
  my_split <- strsplit(my_condition, "_")[[1]] #|\\=
  # extract parameters
  change_what <- my_split[1]
  pos_interval <- NA
  strat_interval <- NA
  assign(paste0(change_what, "_interval"), as.numeric(my_split[2]))
  is_scaled <- my_split[3]
  init_strat <- my_split[4]
  init_pos <- my_split[5]
  male_dist <- as.numeric(my_split[6])
  num_males <- as.numeric(my_split[7])
  

  lookup_table <- rbind(lookup_table, 
                        data.frame(directory=my_condition,
                                   change_what=change_what,
                                   pos_interval=pos_interval,
                                   strat_interval=strat_interval,
                                   is_scaled=is_scaled,
                                   init_strat=init_strat,
                                   init_pos=init_pos,
                                   male_dist=male_dist,
                                   num_males=num_males))
}
```

```{r}
all_results <- tibble()
for (my_condition in conditions){
  # read and load each result
  my_dir_results <- paste0("../to_store/", my_condition, "/results/")
 my_results <- list.files(my_dir_results)
 if (length(my_results) > 0){
   # process a single file
   for (my_file in my_results) {
     my_rnd_seed <- as.numeric(strsplit(my_file, "_")[[1]][2])
     tmp <- read_csv(paste0(my_dir_results, my_file), col_types = cols()) %>% add_column(rnd_seed = my_rnd_seed, directory = my_condition, is_selection=1)

     all_results <- rbind(all_results, tmp)
   }
 }
}

for (my_condition in conditions){
  # read and load each result
  my_dir_nulls <- paste0("../to_store/", my_condition, "/nulls/")
 my_nulls <- list.files(my_dir_nulls)
 if (length(my_nulls) > 0){
   # process a single file
   for (my_file in my_nulls) {
     my_rnd_seed <- as.numeric(strsplit(my_file, "_")[[1]][2])
     tmp <- read_csv(paste0(my_dir_nulls, my_file), col_types = cols()) %>% add_column(rnd_seed = my_rnd_seed, directory = my_condition, is_selection=0)

     all_results <- rbind(all_results, tmp)
   }
 }
}

all_results <- all_results %>% inner_join(lookup_table)
```
```{r}
#ideas: var in interbower distance over time, var in matings over time

```



```{r}
mvovergen <- all_results %>% group_by(rnd_seed,gen,directory, is_selection, is_scaled) %>% summarise(mate_var=var(successful_mating))
```

```{r}
wrap <- function(vec, interval){
  return(c(vec[(length(vec)+1-interval):length(vec)],
           lag(vec, interval)[-(1:interval)]))
}

posvarovergen <- all_results %>% group_by(rnd_seed,gen,directory, is_selection, is_scaled) %>%
 mutate(distfrom0=abs(position-wrap(position,1))) %>%
mutate(distfrom1=abs(position-wrap(position,2))) %>%
mutate(distfrom2=abs(position-wrap(position,3))) %>%
mutate(distfrom3=abs(position-wrap(position,4))) %>%
mutate(distfrom4=abs(position-wrap(position,5))) %>% summarise(var=var(c(distfrom0,distfrom1,distfrom2,distfrom3, distfrom4)))
#we don't divide by the mean here bc it (male_dist) doesn't vary


```




```{r}
modpos <- lm(var ~ is_selection+is_scaled,
              data = filter(posvarovergen, gen==1999))
summary(modpos)

#so it's not driving dispersion (hmmmm)
```
```{r}
pl <- ggplot(data = posvarovergen) + aes(x = gen, y = var, color = as.factor(is_selection)) + geom_line( alpha=.2)+ stat_smooth() + facet_wrap(~is_scaled)
pl


#MAYBE THERE'S A BETTER MEASURE!!! LIKE HOW MANY ARE IN A 6th of a circle
```


```{r}
mod <- lm(mate_var ~ is_selection+is_scaled,
              data = filter(mvovergen, gen==1999))
summary(mod)
#interesting -- perhaps it doesn't affect mate_var significantly in turn
```

```{r}
newmvovg <- mvovergen %>% filter(gen==1999) %>% group_by(is_selection, is_scaled) %>% summarise(a_mv=mean(mate_var)) %>% ungroup() %>% select(a_mv, is_selection, is_scaled) %>% distinct()
```

```{r}
mod2 <- lm(a_mv ~ is_selection+is_scaled,
              data = newmvovg)
summary(mod2)

#note -- still not significant
```


```{r}
scaled = mvovergen %>% filter(directory=='pos_0.1_1_All.VHigh_EvenTenthClumped_900_6')
```



```{r}
pl <- ggplot(data = scaled%>% filter(gen<10)) + aes(x = gen, y = mate_var, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2)
pl

#now the matings are a result
```

```{r}
pl <- ggplot(data = scaled%>%filter(is_selection==1)) + aes(x = gen, y = mate_var, alpha=.2) + geom_point()# , color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2)
pl

```

```{r}

dat <-scaled%>%filter(is_selection==1)
model<-lm(mate_var~gen,data = dat) #is there an error here?
summary(model)


#significantly negative slope -- mating success variance is going down with generations *slightly*

#but does this tell us anything on it's own? I think we need to know if this slope is significantly different from the slope of for the null (once we fix the mating success). In both, we expect the birds to be spreading out regardless and that could be causing it

#also, the relationship probably something more like a saturation curve. It's not going to be a line.

```

```{r}
strat_scaled = mvovergen %>% filter(directory=='strat_0.75_1_All.High_UniformJittered_900_6')
#this was a real quick example: 2 simulations, 100 gens
```

```{r}
pl <- ggplot(data = strat_scaled) + aes(x = gen, y = mate_var, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2)
pl

#is_selection 0 and 1 potentially look the same
#but really we need more than 2 simulations
```

```{r}
stratovergen <- all_results %>% group_by(rnd_seed,gen,directory, is_selection) %>% summarise(avg_strat=mean(probability_maraud)) %>% filter(directory=='strat_0.75_1_All.High_UniformJittered_900_6')

```

```{r}
pl <- ggplot(data = stratovergen) + aes(x = gen, y = avg_strat, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2)
pl

#same story as before

```

```{r}
library(tidyverse)
files <- list.files("../to_run/complete_results/")
conditions <- str_remove(str_remove(files[str_detect(files, "res_00_")],  "res_.._"), ".csv")

```

```{r}
lookup_table <- data.frame()
for (my_condition in conditions){
  # split the string
  my_split <- strsplit(my_condition, "_")[[1]] #|\\=
  # extract parameters
  change_what <- my_split[1]
  pos_interval <- NA
  strat_interval <- NA
  assign(paste0(change_what, "_interval"), as.numeric(my_split[2]))
  is_scaled <- my_split[3]
  init_strat <- my_split[4]
  init_pos <- my_split[5]
  male_dist <- as.numeric(my_split[6])
  num_males <- as.numeric(my_split[7])
  

  lookup_table <- rbind(lookup_table, 
                        data.frame(directory=my_condition,
                                   change_what=change_what,
                                   pos_interval=pos_interval,
                                   strat_interval=strat_interval,
                                   is_scaled=is_scaled,
                                   init_strat=init_strat,
                                   init_pos=init_pos,
                                   male_dist=male_dist,
                                   num_males=num_males))
}
```

```{r}
all_results <- tibble()
my_dir_results <- "../to_run/29_res/"
my_results <- list.files("../to_run/29_res/")
count=1
for (my_file in my_results) {
  my_condition <- str_remove(str_remove(str_remove(my_file, "null_.._"), "res_.._"), ".csv")
  my_rnd_seed <- as.numeric(strsplit(my_file, "_")[[1]][2])
  tmp <- read_csv(paste0(my_dir_results, my_file), col_types = cols()) %>% add_column(rnd_seed = my_rnd_seed, directory = my_condition, is_selection=(count>60))
  all_results <- rbind(all_results, tmp)
  count <-count+1
}
all_results <- all_results %>% inner_join(lookup_table) 
#all_results2 <- all_results %>% filter(gen<750) #different lengths, so we're putting them all at the same length

```
```{r}
mvovergen <- all_results %>% filter(num_males==6) %>% group_by(rnd_seed,gen,directory, is_selection, is_scaled, male_dist) %>% summarise(mate_var=var(successful_mating))
```

```{r}
mod <- lm(mate_var ~ is_selection*is_scaled*male_dist,
              data = filter(mvovergen, gen==1999))
summary(mod)
```

duplicate
```{r}
mvovergen <- all_results %>% filter(num_males==6) %>% group_by(rnd_seed,gen,directory, is_selection, is_scaled, male_dist) %>% summarise(mate_var=var(successful_mating))
```

```{r}
mod <- lm(mate_var ~ is_selection*is_scaled*male_dist,
              data = filter(mvovergen, gen==1999))
summary(mod)
```


```{r}
stratovergen <- all_results %>%
  group_by(gen, is_selection, male_dist, is_scaled, rnd_seed, num_males) %>%
  summarise(avg_strat=mean(probability_maraud)) %>%
  ungroup() %>%
  group_by(is_selection, male_dist, is_scaled, rnd_seed, num_males) %>%
  mutate(d_avg_strat=avg_strat-lag(avg_strat)) %>% mutate(l_avg_strat=lag(avg_strat)) %>%
  ungroup()

#not doing this rn!
```
all the variables that might matter (we'll handle combinations thereof in a second):
-gen
-is_selection
-male_dist
-sim*condition*is_selection (not really sim on it's own tho)
-lag time variables (figure out how to assess how far back autoregression goes with a test of some sort... the issue is that there are multiple time series)... could the lag variable actually take into account the above bullet point? probably!

Note: is it still not stationary? Prob not
```{r}
library(tidyverse) # this loads both dplyr and tidyr, along with other packages
library(fpp2) # time series forecasting
library(lubridate)
library(GGally)
names <- c() #rep(NA, 2*3*10)
gen_shifts <- c() #rep(NA, 2*3*10)
for(is_s in c(TRUE, FALSE)){
  for(m_d in c(300, 600, 900)){
    for(is_sc in c(0,1)){
      temp <- stratovergen %>% filter(is_selection==is_s) %>% filter(male_dist==m_d) %>% filter(is_scaled==is_sc) 
      temp1 <- temp %>% group_by(gen) %>%  summarise(d_avg_avg_strat=mean(d_avg_strat)) %>% ungroup()
      cond_ts <- select(temp1, d_avg_avg_strat) 
      # p <- ggAcf(cond_ts, lag.max = 1999)
      # print(p)
      for(rnd in 0:9){
        temp2 <- temp %>% filter(rnd_seed==rnd)
        name <- paste0(rnd, "_", is_s, "_", is_sc, "_", m_d)
        assign(name, select(temp2, d_avg_strat))
        # p <- ggAcf(get(name)) + ggtitle(name)
        # print(p)
        # g <- ccf(na.omit(get(name)), na.omit(cond_ts), lag.max = 100)
        # print(g)
        #names=c(names, name)
        #gen_shifts=c(gen_shifts, sum(g$acf>.05))
      }
    }
  }
}


```

```{r}
# new <- stratovergen %>% group_by(is_selection, male_dist, rnd_seed)
# 
# 
# new <- new %>% mutate(lags = map(new, function(dat){
#     
#     
# 
# 
# df %>% nest(-cats) %>% 
#     mutate(lags = map(data, function(dat) {
#         imap_dfc(dat[-1], ~set_names(map(1:2, lag, x = .x), 
#                                      paste0(.y, '_lag', 1:2)))
#         })) %>% 
#     unnest() %>% 
#     arrange(days)

```


```{r}
library(tseries)
adf.test(residuals.glm(model2))
```



```{r}
model5 <- glm(avg_strat ~ is_selection+male_dist+is_scaled,
              data = stratovergen %>% filter(gen==1999 & num_males==6),
              family = "gaussian")
summary(model5)
#different results when you use + vs *!!!!!


#removing male_dist lowers AIC (slightly)

#don't get AIC.... hmmm
```
```{r}
newsovg <- stratovergen %>% filter(gen==1999) %>% group_by(is_selection, male_dist, is_scaled) %>% summarise(aa_strat=mean(avg_strat)) %>% ungroup() %>% select(aa_strat, is_selection, male_dist, is_scaled) %>% distinct()

```

```{r}
model6 <- lm(aa_strat ~ is_selection+male_dist+is_scaled,
              data = newsovg)
summary(model6)

#removing male_dist lowers AIC (slightly)
```

```{r}
model7 <- lm(aa_strat ~ is_selection, data = newsovg)
summary(model7)

#AIC is worse (higher)
#Adj R^2 is best I've found (but idk R^2 for glms)
```


NEW THING
```{r}
library(tidyverse)
files <- list.files("../to_run/complete_results/")
conditions <- str_remove(str_remove(files[str_detect(files, "res_00_")],  "res_.._"), ".csv")

```

```{r}
lookup_table <- data.frame()
for (my_condition in conditions){
  # split the string
  my_split <- strsplit(my_condition, "_")[[1]] #|\\=
  # extract parameters
  change_what <- my_split[1]
  pos_interval <- NA
  strat_interval <- NA
  assign(paste0(change_what, "_interval"), as.numeric(my_split[2]))
  is_scaled <- my_split[3]
  init_strat <- my_split[4]
  init_pos <- my_split[5]
  male_dist <- as.numeric(my_split[6])
  num_males <- as.numeric(my_split[7])
  

  lookup_table <- rbind(lookup_table, 
                        data.frame(directory=my_condition,
                                   change_what=change_what,
                                   pos_interval=pos_interval,
                                   strat_interval=strat_interval,
                                   is_scaled=is_scaled,
                                   init_strat=init_strat,
                                   init_pos=init_pos,
                                   male_dist=male_dist,
                                   num_males=num_males))
}
```

```{r}
all_results <- tibble()
my_dir_results <- "../to_run/complete_results/"
my_results <- list.files("../to_run/complete_results/")
count=1
for (my_file in my_results) {
  my_condition <- str_remove(str_remove(str_remove(my_file, "null_.._"), "res_.._"), ".csv")
  my_rnd_seed <- as.numeric(strsplit(my_file, "_")[[1]][2])
  tmp <- read_csv(paste0(my_dir_results, my_file), col_types = cols()) %>% add_column(rnd_seed = my_rnd_seed, directory = my_condition, is_selection=(count>30))
  all_results <- rbind(all_results, tmp)
  count <-count+1
}
all_results <- all_results %>% inner_join(lookup_table) 
#all_results <- all_results %>% filter(gen<750) #different lengths, so we're putting them all at the same length

```

```{r}
mvovergen <- all_results %>% group_by(rnd_seed,gen,directory, is_selection, male_dist) %>% summarise(mate_var=var(successful_mating))

stratovergen <- all_results %>% group_by(rnd_seed,gen,directory, is_selection, male_dist) %>% summarise(avg_strat=mean(probability_maraud))
```

```{r}
model <- lm(mate_var ~ is_selection*male_dist,
              data = mvovergen %>% filter(gen==1999))
summary(model)
```

```{r}
model <- lm(avg_strat ~ is_selection*male_dist,
              data = stratovergen %>% filter(gen==1999))
summary(model)
```
```{r}
model <- lm(avg_strat ~ is_selection,
              data = stratovergen %>% filter(gen==1999 & male_dist==300))
summary(model)
#just with male_dist=300 it still doesn't work!
```

```{r}
pl <- ggplot(data = filter(stratovergen, male_dist==300)) + aes(x = gen, y = avg_strat, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2) + geom_line()
pl
```
```{r}
pl <- ggplot(data = stratovergen) + aes(x = gen, y = avg_strat, color = as.factor(is_selection))  + stat_smooth() + facet_wrap(~male_dist)
pl
```

glm binomial won't work!!! assumes it levels off at 1!
```{r}
pl <- ggplot(data = stratovergen %>% filter(male_dist==600)) + aes(x = gen, y = avg_strat, color = as.factor(is_selection))  + stat_smooth()
pl
```

```{r}
pl <- ggplot(data = stratovergen %>% filter(male_dist==300)) + aes(x = gen, y = avg_strat, color = as.factor(is_selection))  + stat_smooth() + facet_wrap(~male_dist)
pl
```

```{r}
sog300 <- stratovergen %>% filter(male_dist==300)
SS<-getInitial(avg_strat~SSlogis(gen,alpha,log(alpha/.1-1)*scale,scale),data=sog300)
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<- .01

```


```{r}
library(nlme)
#the formula for the models
lF<-formula(avg_strat~K*.01*exp(r*gen)/(K+.01*(exp(r*gen)-1)) | is_selection)

#fit the model
(m <- nlsList(lF,data=sog300,start=list(K=K_start,r=R_start)))
```

```{r}
#the formula for the models
lF<-formula(avg_strat~K*.01*exp(r*gen)/(K+.01*(exp(r*gen)-1)) | is_selection)

sog300 <- stratovergen %>% filter(male_dist==300)
SS<-getInitial(avg_strat~SSlogis(gen,alpha,log(alpha/.1-1)*scale,scale),data=sog300)
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<- .01
#fit the model
(m <- nlsList(lF,data=sog300,start=list(K=K_start,r=R_start)))
sog300 <- sog300 %>% arrange(is_selection, rnd_seed)
sog300$pred <- predict(m)



sog600 <- stratovergen %>% filter(male_dist==600)
SS<-getInitial(avg_strat~SSlogis(gen,alpha,log(alpha/.1-1)*scale,scale),data=sog600)
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<- .01
#fit the model
(m <- nlsList(lF,data=sog600,start=list(K=K_start,r=R_start)))
sog600 <- sog600 %>% arrange(is_selection, rnd_seed)
sog600$pred <- predict(m)



sog900 <- stratovergen %>% filter(male_dist==900)
SS<-getInitial(avg_strat~SSlogis(gen,alpha,log(alpha/.1-1)*scale,scale),data=sog900)
K_start<-SS["alpha"]
R_start<-1/SS["scale"]
N0_start<- .01
#fit the model
(m <- nlsList(lF,data=sog900,start=list(K=K_start,r=R_start)))
sog900 <- sog900 %>% arrange(is_selection, rnd_seed)
sog900$pred <- predict(m)


sog <- rbind(sog300, sog600, sog900)

mlabs <- c("300m", "600m", "900m")

pl <- ggplot(data = sog) + aes(x = gen, y = avg_strat, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection))  + geom_line( alpha=.2)  + geom_line(aes(y=pred), size=1) + facet_wrap(~male_dist) + labs(x="Generation", y="Average strategy", title="Strategy evolution varying density") +  theme_bw() + theme(legend.position="None") + theme(axis.text.x = element_text(angle = 45, hjust=1))
pl

```
```{r}

confint(m) #profiling approach... look into it
```


```{r}
pl <- ggplot(data = stratovergen %>% filter(male_dist==300)) + aes(x = gen, y = avg_strat, color = as.factor(is_selection)) + geom_point(alpha=.05)
pl
```

```{r}
pl <- ggplot(data = filter(stratovergen, male_dist==300)) + aes(x = gen, y = avg_strat, color = as.factor(is_selection), group=interaction(rnd_seed,is_selection)) + geom_line( alpha=.2) + geom_line(predict(m))
pl
```

